### 2024-04-08 docs/SOSP 2024/intro.tex
Add abstract and XGB comparison

\section{Introduction}
\label{sec:intro}
We are in the midst of a hardware revolution, a new golden age for computer architecture~\cite{TuringLecture}. The last decade has seen a shift in architectural paradigms, with the rise of GPUs and accelerators. This shift has been driven by the necessity to innovate in the post Moore's law and Dennard's scaling era. This transformation has also played a significant role in the success of modern deep learning models, as they enable scaling model training and inference to a massive number of threads. Such scalability would be essential for all performance critical applications, including other machine learning models that need to scale with increasing data sizes and model complexities. 
%need to accelerate machine learning workloads. The success of modern AI models is due to their ability to scale both training and inference to a massive number of threads. This has been made possible by the rise of GPUs and accelerators.

%Despite these recent advancements, one dominant family of models, namely decision forest models have not seen the same level of acceleration.
Decision forest models remain the mainstay for machine learning over tabular data~\cite{tabular}. 
Their robustness, interpretability, and ability to handle missing data make them a popular choice for a wide range of applications. 
\TODO{a few more lines, classification, regression, etc.}
%We observe that while scalable performance on neural network models has received significant attention, decision tree inference has not seen the same level of acceleration.
A recent survey~\cite{kaggle}\dots. 
The survey also finds that, the cost of inference is the most critical factor in the overall cost of deploying a machine learning model.
This is because, in production settings, each model is trained once and often used for inference a few thousand times. 
%

>>>>

\section{Introduction}
\label{sec:intro}
We are in the midst of a hardware revolution, a new golden age for computer architecture~\cite{GoldenAge}. The last 
decade has seen a shift in architectural paradigms, with the rise of GPUs and accelerators. This shift has been driven
by the necessity to innovate in the post Moore's law and Dennard's scaling era. This transformation has also played 
a significant role in the success of modern deep learning models, as they enable scaling model training and inference 
to a massive number of threads. Such scalability would be essential for all performance critical applications, including
other machine learning models that need to scale with increasing data sizes and model complexities. 
%need to accelerate machine learning workloads. The success of modern AI models is due to their ability to scale both training and inference to a massive number of threads. This has been made possible by the rise of GPUs and accelerators.

%Despite these recent advancements, one dominant family of models, namely decision forest models have not seen the same level of acceleration.
Decision forest models remain the mainstay for machine learning over tabular data~\cite{DLNotAllYouNeed,TreebasedOutperformDL}. 
Their robustness, interpretability, and ability to handle missing data make them a popular choice for a wide range of applications. 
\TODO{a few more lines, classification, regression, etc.}
%We observe that while scalable performance on neural network models has received significant attention, decision tree inference has not seen the same level of acceleration.
A recent survey~\cite{kaggle}\dots. 
The survey also finds that, the cost of inference is the most critical factor in the overall cost of deploying a machine learning model.
This is because, in production settings, each model is trained once and often used for inference a few thousand times. 
%
